Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-12-17 paper-proposal.tex
edit

% MAIN CONTENT
% "include a notification if this is an update from a previous publication in the Web Server issue, and in that case, include an estimate of the number of users and the number of citations."
% "For web servers, or essentially similar web servers, that have been the subject of a previous publication, including publication in journals other than NAR, there is a minimum two-year interval before re-publication in the Web Server Issue."
Our proposal covers an update to Superphy \cite{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.
The update, called Spfy, adds real-time subtyping options and uses graph datastructures to store and retrieve results for additional analyses.
% I'm unsure if we should add more about the subtyping options. For example, see:
% https://github.com/superphy/paper_platform/commit/c017b1e022d310e16a1433af9d58a73e9550a401
Many of the comparative analyses that are run on current workflows chain different software, but lack storage methods which understand the relations between results.
% "IF THE WEBSITE IMPLEMENTS A META-SERVER OR COMPUTATIONAL WORKFLOW, the summary MUST describe 1) significant added value beyond the simple chaining together of existing third party software or the calculation of a consensus prediction from third party predictors and classifiers; and at least one of the following: 2) how user time for data gathering and multi-step analysis is significantly reduced, or 3) how the website offers significantly enhanced display of the data and results."
By making the storage and retrieval of results part of the platform, and effectively linked to the organisms of interest with a standardized ontology, we can mitigate the recomputing of analyses. Unlike other methods, graph storage enables comparitive analyses between results generated from any of platform's modules.
Integrated data storage will be necessary as whole genome sequencing (WGS) data for bacterial pathogens have accumulated in public databases in the tens of thousands, with hundreds of thousands set to be available within the next few years.

>>>>

% MAIN CONTENT
% "include a notification if this is an update from a previous publication in the Web Server issue, and in that case, include an estimate of the number of users and the number of citations."
% "For web servers, or essentially similar web servers, that have been the subject of a previous publication, including publication in journals other than NAR, there is a minimum two-year interval before re-publication in the Web Server Issue."
Our proposal covers an update to Superphy \cite{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.
The update, called Spfy, adds real-time subtyping options and uses graph datastructures to store and retrieve results for additional analyses.
% I'm unsure if we should add more about the subtyping options. For example, see:
% https://github.com/superphy/paper_platform/commit/c017b1e022d310e16a1433af9d58a73e9550a401
Many of the comparative genomics analysis workflows chain different software, but lack storage methods which capture the relations between results.
% "IF THE WEBSITE IMPLEMENTS A META-SERVER OR COMPUTATIONAL WORKFLOW, the summary MUST describe 1) significant added value beyond the simple chaining together of existing third party software or the calculation of a consensus prediction from third party predictors and classifiers; and at least one of the following: 2) how user time for data gathering and multi-step analysis is significantly reduced, or 3) how the website offers significantly enhanced display of the data and results."
By making the storage and retrieval of results part of the platform, with data effectively linked to the organisms of interest through a standardized ontology, we can mitigate the recomputing of analyses. Graph storage enables direct comparison of analyses results generated from any of platform's modules.
Integrated data storage will be necessary as whole genome sequencing (WGS) data for bacterial pathogens have accumulated in public databases in the tens of thousands, with hundreds of thousands set to be available within the next few years.
